Security on Networks

### 2013-05-14 paper/paper.tex
Moving stuff into the paper subdirectory.

@@

@@

>>>>

\documentclass{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[margin=1.25in]{geometry}

\theoremstyle{plain}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\title{Security on Networks}
\date{\today}
\author{Bonny Jain, John Wang, Iris Xu}

\begin{document}

  \maketitle

@@

The network effect starts to increase to something significant by $q = 0.5$, then falls off again after $q = 0.8$. The fall off in the network effect comes from the saturation of protection levels. After a certain point, the marginal benefit of extra protection starts to decrease because of the difficulty of actually spreading the infection.

@@

\end{document}
